Thesis Proposal

### 2019-09-30 ThesisProposal_GV.Rmd
add suggestions

The numerous assumptions underlying MI algorithms can principally not be verified from the incomplete observed data (**source?**). Instead, imputers are  designated to evaluate the (plausibility of) multiply imputed data, and the robustness of results to the assumptions. The latter can be assessed by performing sensitivity analyses, see e.g. @nguy17 for practical guidelines. Methodology for evaluating the MI data however, is still largely missing. In the only available review of diagnostics, @abay08 overlook the most vital state to be evaluated: convergence of the algorithm. Without convergence, any 'deeper' assumption and resulting inference is invalid (**source?**).
<!-- The weighting approach (a selection based method) [25,26], and the pattern-mixture approach [25,27] are two methods that have been proposed in the literature for conducting sensitivity analyses within the MI framework. (https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-015-0022-1) -->

>>>>

The numerous assumptions underlying MI algorithms can principally not be verified from the incomplete observed data **No source needed - we'd need the true data to verify**. Instead, imputers are  designated to evaluate the (plausibility of) multiply imputed data, and the robustness of results to the assumptions. The latter can be assessed by performing sensitivity analyses, see e.g. @nguy17 for practical guidelines. Methodology for evaluating the MI data however, is still largely missing. In the only available review of diagnostics, @abay08 overlook the most vital state to be evaluated: convergence of the algorithm. Without convergence, any 'deeper' assumption and resulting inference may be (anders erg sterk) invalid.
<!-- The weighting approach (a selection based method) [25,26], and the pattern-mixture approach [25,27] are two methods that have been proposed in the literature for conducting sensitivity analyses within the MI framework. (https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-015-0022-1) -->
